---
title: "reproducing-redlining"
author: "Sal Balkus"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

# Reproducing "The Lasting Legacy of Redlining"

This notebook attempts to reproduce the figures in the FiveThirtyEight article "[The Lasting Legacy of Redlining](https://projects.fivethirtyeight.com/redlining/)" originally authored by Ryan Best and Elena Mejía.

```{r, include=F}
set.seed(10)
library(tidyverse)
library(tidycensus)
library(sp)
library(sf)
library(grid)
library(ggplotify)
library(ggmap)
library(smoothr)
library(plyr)
library(doParallel)
library(foreach)
library(plotly)
library(scatterpie)
library(ggforce)
library(stats)
library(gridExtra)
```

## Step 1: Download Data

We obtain the project data from the FiveThirtyEight GitHub.

```{r, include = FALSE}

# Where in the repository to save the data
dest1 <- "../data/metro-grades.csv"
dest2 <- "../data/zone-block-matches.csv"

# Download files if they do not already exist
# TODO: Allow regeneration of these files using a driver script
if(!file.exists(dest1)){
  source1 <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/redlining/metro-grades.csv"
  download.file(url = source1, destfile = dest1)
} else {
  metro_grades <- read_csv(dest1)
}

if(!file.exists(dest2)){
  source2 <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/redlining/zone-block-matches.csv"
  download.file(url = source2, destfile = dest2)
} else {
  zone_matches <- read_csv(dest2)
}


```

## Step 2: Obtain Census Data

Use the `tidycensus` package to load shape files and 2020 census data.

*This product uses the Census Bureau Data API but is not endorsed or certified by the Census Bureau.*

```{r}
# Cache shapefiles
options(tigris_use_cache = TRUE)

# Get race data with shape files
# TODO: Allow regeneration of these files using the driver script.
# TODO: Allow users to invoke census API

blocks_file <- "../data/blocks.rds"

if(!file.exists(blocks_file)){
  blocks <- get_decennial(geography = "block", 
                          state="Pennsylvania",
                          variables = c("P2_001N", # Total
                                        "P2_002N", # Total Hispanic or Latino
                                        "P2_005N", # Total Non-Hispanic White
                                        "P2_006N", # Total Non-Hispanic Black
                                        "P2_007N", # Total Non-Hispanic Indian
                                        "P2_008N", # Total Non-Hispanic Asian
                                        "P2_009N", # Total Non-Hispanic Islander
                                        "P2_010N", # Total Non-Hispanic Other
                                        "P2_011N"), # Total Non-Hispanic two or more races
                          year = 2020, geometry = TRUE) %>% 
    pivot_wider(names_from = variable, values_from = value)

  # Manually cache the data to avoid downloading again
  saveRDS(blocks, file = "../data/blocks.rds")
} else {
  blocks <- read_rds(blocks_file)
}


states <- get_decennial(geography = "state", 
                         variables = c("STATE"), 
                         year = 2020, geometry = TRUE)

# Get the total geography of each metro area
metros <- get_decennial(geography = "cbsa", 
                         variables = c("P2_001N"), 
                         year = 2020, geometry = TRUE)
metros$NAME <- substr(metros$NAME, 1, nchar(metros$NAME)-11) # The 538 data has "Metro Area" and "Micro Area" removed from NAME
metro_grades <- left_join(metro_grades, metros, by=c("metro_area"="NAME")) # associate each metro area with a geography
metro_grades$centroid <- st_centroid(metro_grades$geometry)



# Filter for the blocks mapped by HOLC
holc_blocks <- inner_join(zone_matches, blocks, by=c("block_geoid20"="GEOID"))

# Select and reformat Pittsburgh
pitt <- holc_blocks %>% filter(holc_city == "Pittsburgh")

```

## Step 3: Clean data to restrict to 10 percent buffer boundary

```{r, include=F}

# Construct a circle around the centroid of the given area, with a percentage buffer
circumscribe <- function(df, pct=0.1){
  geo <- df %>% st_as_sf() %>% arrange(block_geoid20)
  # Compute the convex hull
  hull <- geo %>% st_convex_hull()
  
  # Compute centroids
  geo_center <- st_centroid(hull)
  
  # Add centroid, then cast hull to points
  hull_points <- hull %>% 
      mutate(centroid_geometry = geo_center$geometry) %>%
      st_cast("POINT")
  
  # Compute distance from centroid to all points in hull
  hull_points$dist_to_centroid <- as.numeric(hull_points %>% 
                                                 st_distance(hull_points$centroid_geometry, by_element = TRUE))
  
  # Pick the hull point the furthest distance from the centroid
  hull_max <- hull_points %>% 
      arrange(block_geoid20) %>%
      group_by(block_geoid20) %>%
      summarize(max_dist = max(dist_to_centroid)) %>% 
      ungroup()
  
  
  # Draw a circle using that distance
  diam <- hull_max$max_dist * (1 + pct)
  geo_circumscribed <- smooth(st_buffer(geo_center, diam), method="ksmooth", smoothness=10)
  return(geo_circumscribed)
}

### Calculate the geometric difference and compute the percentage of each census block contained within the bound

# Combine into one shape for circumscribing
combined_geo <- pitt %>% summarize(st_combine(geometry))
colnames(combined_geo) <- "geometry"
combined_geo$block_geoid20 <- "1"
# Draw a circle with 10% buffer around the HOLC region
bound <- circumscribe(combined_geo)



# Perform geometric calculations and save to file
filtered_blocks_file <- "../data/blocks_buffer.rds"
if(!file.exists(filtered_blocks_file)){
  
  # First filter out all blocks which do not intersect the circular bound
  # Then, crop all blocks to the bound
  # Finally, calculate area of each block remaining in the bound
  blocks_buffer <- blocks %>% 
    filter(st_intersects(geometry, bound, sparse=F)) %>% 
    mutate(geometry2 = st_intersection(geometry, bound)) %>% 
    mutate(pct_area = st_area(geometry2) / st_area(geometry))
  
  saveRDS(blocks_buffer, filtered_blocks_file)
} else{
  blocks_buffer <- read_rds(filtered_blocks_file)
  blocks_buffer$pct_area <- as.numeric(blocks_buffer$pct_area)

}



```

## Step 4: Construct the map of the surrounding area

```{r, warning = F, include=F}

# Randomly sample a point in each block for each corresponding race
# TODO: It's not clear how the authors handled fractional people created from cropping census blocks

blocks_buffer <- mutate(blocks_buffer, 
                        hispanic = round(P2_002N*pct_area),
                        white = round(P2_005N*pct_area),
                        black = round(P2_006N*pct_area),
                        asian = round(P2_008N*pct_area),
                        other_race = round((P2_007N + P2_009N + P2_010N + P2_011N)*pct_area)
                        )
samp <- blocks_buffer %>% 
  mutate(
    hispanic = round(hispanic/10),
    white = round(white/10),
    black = round(black/10),
    asian = round(asian/10),
    other_race = round(other_race/10)
)

# For some reason the Fibonacci sampling does not work properly. I should consider submitting an Issue on GitHub

hispanic_path <- "../data/sampled_hispanic.rds"
if(!file.exists(hispanic_path)){
  samp_hispanic <- samp %>% filter(hispanic > 0)
  output <- st_sample(samp_hispanic$geometry2, samp_hispanic$hispanic, type="random", exact=F)
  saveRDS(output, file = hispanic_path)
}
points_hispanic <- read_rds(hispanic_path)

other_path <- "../data/sampled_other.rds"
if(!file.exists(other_path)){
  samp_other <- samp %>% filter(other_race > 0)
  output <- st_sample(samp_other$geometry2, samp_other$other_race, type="random", exact=F)
  saveRDS(output, file = other_path)
}
points_other <- read_rds(other_path)

asian_path <- "../data/sampled_asian.rds"
if(!file.exists(asian_path)){
  samp_asian <- samp %>% filter(asian > 0)
  output <- st_sample(samp_asian$geometry2, samp_asian$asian, type="random", exact=F)
  saveRDS(output, file = asian_path)
}
points_asian <- read_rds(asian_path)


black_path <- "../data/sampled_black.rds"
if(!file.exists(black_path)){
  samp_black <- samp %>% filter(black > 0)
  output <- st_sample(samp_black$geometry2, samp_black$black, type="random", exact=F)
  saveRDS(output, file = black_path)
}
points_black <- read_rds(black_path)

white_path <- "../data/sampled_white.rds"
if(!file.exists(white_path)){
  samp_white <- samp %>% filter(white > 0)
  output <- st_sample(samp_white$geometry2, samp_white$white, type="random", exact=F)
saveRDS(output, file = white_path)
}
points_white <- read_rds(white_path)

# Use the previously-calculated bound to create an opaque square with a circular cutout
# This masks the square ggmap, only displaying the inner circle
extent <- st_bbox(bound)
outside <- st_as_sfc(extent)
inside <- bound$geometry[1]
cutout <- st_difference(outside, inside)

# Download a basemap for Pittsburgh from ggmap
extent <- c(left = extent[["xmin"]], bottom = extent[["ymin"]], right = extent[["xmax"]], top = extent[["ymax"]])
m <- get_stamenmap(extent, zoom=10, maptype = "toner-background")

# Display the map
points <- data.frame(race = c("white", "black", "hispanic", "asian", "other"), 
                     geometry=c(st_combine(points_white), 
                                st_combine(points_black), 
                                st_combine(points_hispanic), 
                                st_combine(points_asian), 
                                st_combine(points_other)), 
                     color=c("#ffb262", "#129e56","#7570b3","#e7298a", "#43a8b5"))
points$race <- factor(points$race, levels = points$race, ordered=T)
pt_sz <- 0.001

surrounding_area <- ggmap(m) +
  geom_sf(data = cutout, mapping = aes(geometry=geometry), color="white", fill="white", inherit.aes = FALSE) +
  geom_sf(data = bound, mapping = aes(geometry=geometry), color="black", fill=NA, lwd = 0.5, inherit.aes = FALSE) +
  geom_sf(data = points, mapping = aes(geometry=geometry, color=race), size=0.001, alpha=0.5, inherit.aes = FALSE, show.legend=F) + 
  scale_color_manual(values = points$color) +
  labs(title = "Pittsburgh's Surrounding Area") +
  theme_void() + theme(plot.title=element_text(margin = margin(b=10), hjust = 0.45))

PA <- states %>% filter(NAME == "Pennsylvania")

city_loc <- data.frame(geometry=c((metro_grades %>% filter(metro_area == "Pittsburgh, PA"))$centroid[1]))

PA_plot <- ggplot() + 
  geom_sf(data = PA, mapping = aes(geometry=geometry)) +
  geom_sf(data = city_loc, mapping = aes(geometry=geometry), size=5, color="black") + 
  geom_sf(data = city_loc, mapping = aes(geometry=geometry), size=3, color="darkgray") + 
  theme_void()

#ggsave("../results/pitt_surrounding.png")



```
### Bar Plots

```{r, warning=F}

surrounding_counts <- blocks_buffer %>% 
  summarize(white = sum(white),
            black = sum(black),
            hispanic = sum(hispanic),
            asian = sum(asian),
            other = sum(other_race))
surrounding_pct <- as.data.frame(t(round(surrounding_counts / sum(surrounding_counts), digits = 3)*100))
colnames(surrounding_pct) <- "Percentage"
surrounding_pct$Race <- c("White", "Black", "Latino", "Asian", "Other")
surrounding_pct$Race <- factor(surrounding_pct$Race, levels=rev(c("White", "Black", "Latino", "Asian", "Other")), ordered = T)
surrounding_pct$tmp <- factor("1", level=c("0","1"))
surrounding_pct$tmp_lab <- factor("1", level=c("0","1"))
surrounding_pct$label_loc <- cumsum(surrounding_pct$Percentage) - surrounding_pct$Percentage / 2
surrounding_pct$label <- paste(surrounding_pct$Race, " - ", surrounding_pct$Percentage, "%", sep="")

p <- ggplot() + geom_bar(data=surrounding_pct, aes(x = Percentage, y = tmp, fill = Race), color="white", lwd=1, width=0.2, stat="identity", show.legend=F) +
  geom_text(data=filter(surrounding_pct, Race %in% c("White", "Black")), aes(x = label_loc, y = tmp_lab, label = label), position = position_nudge(x = 0, y = -0.15), size = 4) +
  theme_void() +
  scale_fill_manual(values = rev(points$color))

surrounding_bar <- ggplotly(p, tooltip = c("Percentage", "Race"), width = 800, height = 200) %>%
  layout(
    showlegend = F, 
    legend = list(orientation = 'h'),
    yaxis = list(
            color = '#ffffff',
            gridcolor = '#ffff'),
    xaxis = list(
            color = '#ffffff',
            gridcolor = '#ffff')
  )


```

```{r}
bar_grade <- function(metro_grades, grade){
  holc_pct <- as.data.frame(t(metro_grades %>% 
    filter(metro_area == "Pittsburgh, PA", holc_grade == grade) %>% 
    select(pct_white, pct_black, pct_hisp, pct_asian, pct_other)))
  colnames(holc_pct) <- "Percentage"
  holc_pct$Percentage <- round(holc_pct$Percentage, digits = 1)
  holc_pct$Race <- c("White", "Black", "Latino", "Asian", "Other")
  holc_pct$Race <- factor(holc_pct$Race, levels=rev(c("White", "Black", "Latino", "Asian", "Other")))
  holc_pct$Race2 <- holc_pct$Race # Need this so "Race" isn't duplicated due to grouping on ggplot
  holc_pct$tmp <- factor("1", level=c("0","1"))
  holc_pct$tmp_lab <- factor("1", level=c("0","1"))
  holc_pct$label_loc <- cumsum(holc_pct$Percentage) - holc_pct$Percentage / 2
  holc_pct$label <- paste(holc_pct$Race, " - ", holc_pct$Percentage, "%", sep="")

  p <- ggplot() + geom_bar(data=holc_pct, aes(x = Percentage, y = tmp, fill = Race, group = Race2), color="white", lwd=1, width=0.2, position="stack", stat="identity", show.legend=F) +
  geom_text(data=filter(holc_pct, Percentage > 6), aes(x = label_loc, y = tmp_lab, label = label), position = position_nudge(x = 0, y = -0.2), size = 4) +
  theme_void() +
  scale_fill_manual(values = rev(points$color))
  
  holc_bar <- ggplotly(p, tooltip = c("Percentage", "Race"), autosize = F, width = 800, height = 200) %>%
  layout(
    showlegend = F, 
    legend = list(orientation = 'h'),
    yaxis = list(
            color = '#ffffff',
            gridcolor = '#ffff'),
    xaxis = list(
            color = '#ffffff',
            gridcolor = '#ffff')
  )
  
  holc_bar
}
```



### Add Pennsylvania to the plot
```{r, warning = FALSE}

# The grid package allows us to print grobs to the graphics device by manipulating the viewport
# The ggplotify package allows us to turn arbitrary ggplot objects into grobs
# Both of these we use to overlay plots created with geom_sf previously
construct_surrounding_plot <- function(surrounding_area, PA_plot){
  grid.newpage()
  grid.draw(as.grob(surrounding_area))
  # Place Pennsylvania in the correct frame of reference relative to the surrounding area
  sample_vp <- viewport(x = 0.6, y = 0.05, 
                        width = 0.25, height = 0.25,
                        just = c("left", "bottom"),
                        angle = 15)
  pushViewport(sample_vp)
  grid.draw(as.grob(PA_plot))
  popViewport()
}

```




## Step 5: Construct maps of each zone type

```{r, warning = FALSE}
#| out-width: 100%

# Sample from every map grade
map_grade <- function(df, grade){
  samp <- df %>% filter(holc_grade == grade)
  print(sprintf("Saving Hispanic %s...", grade))
  hispanic_path <- sprintf("../data/sampled_hispanic_%s.rds", grade) 
  if(!file.exists(hispanic_path)){
    samp_hispanic <- samp %>% filter(hispanic > 0)
    output <- st_sample(samp_hispanic$geometry2, samp_hispanic$hispanic, type="random", exact=F)
    saveRDS(output, file = hispanic_path)
  }
  points_hispanic <- read_rds(hispanic_path)
  
  print(sprintf("Saving Other %s...", grade))
  other_path <- sprintf("../data/sampled_other_%s.rds", grade)
  if(!file.exists(other_path)){
    samp_other <- samp %>% filter(other_race > 0)
    output <- st_sample(samp_other$geometry2, samp_other$other_race, type="random", exact=F)
    saveRDS(output, file = other_path)
  }
  points_other <- read_rds(other_path)
  
  print(sprintf("Saving Asian %s...", grade))
  asian_path <- sprintf("../data/sampled_asian_%s.rds", grade)
  if(!file.exists(asian_path)){
    samp_asian <- samp %>% filter(asian > 0)
    output <- st_sample(samp_asian$geometry2, samp_asian$asian, type="random", exact=F)
    saveRDS(output, file = asian_path)
  }
  points_asian <- read_rds(asian_path)
  
  print(sprintf("Saving Black %s...", grade))
  black_path <- sprintf("../data/sampled_black_%s.rds", grade)
  if(!file.exists(black_path)){
    samp_black <- samp %>% filter(black > 0)
    output <- st_sample(samp_black$geometry2, samp_black$black, type="random", exact=F)
    saveRDS(output, file = black_path)
  }
  points_black <- read_rds(black_path)
  
  print(sprintf("Saving White %s...", grade))
  white_path <- sprintf("../data/sampled_white_%s.rds", grade)
  if(!file.exists(white_path)){
    samp_white <- samp %>% filter(white > 0)
    output <- st_sample(samp_white$geometry2, samp_white$white, type="random", exact=F)
  saveRDS(output, file = white_path)
  }
  points_white <- read_rds(white_path)
}

holc_samp <- inner_join(zone_matches, samp, by=c("block_geoid20"="GEOID"))

for(grade in c("A","B","C","D")){
  if(!file.exists(sprintf("../data/sampled_white_%s.rds", grade)) ||
  !file.exists(sprintf("../data/sampled_black_%s.rds", grade)) ||
  !file.exists(sprintf("../data/sampled_hispanic_%s.rds", grade)) ||
  !file.exists(sprintf("../data/sampled_asian_%s.rds", grade)) ||
  !file.exists(sprintf("../data/sampled_other_%s.rds", grade))){
    map_grade(holc_samp, grade)
  }
}

# Construct HOLC plots
holc_plots <- list()

grades <- c(A = "Best", B = "Desirable", C = "Declining", D = "Hazardous")

for(i in c("A","B","C","D")){
  points[[i]] <- c(st_combine(read_rds(sprintf("../data/sampled_white_%s.rds", i))),
       st_combine(read_rds(sprintf("../data/sampled_black_%s.rds", i))),
       st_combine(read_rds(sprintf("../data/sampled_hispanic_%s.rds", i))),
       st_combine(read_rds(sprintf("../data/sampled_asian_%s.rds", i))),
       st_combine(read_rds(sprintf("../data/sampled_other_%s.rds", i)))
       )
  
  holc_plots[[i]] <- ggmap(m) +
  geom_sf(data = cutout, mapping = aes(geometry=geometry), color="white", fill="white", inherit.aes = FALSE) +
  geom_sf(data = bound, mapping = aes(geometry=geometry), color="black", fill=NA, lwd = 0.5, inherit.aes = FALSE) +
  geom_sf(data = points, mapping = aes(geometry=.data[[i]], color=race), size=0.01, inherit.aes = FALSE, show.legend=F) + 
  labs(title = sprintf("Pittsburgh's %s Zones", grades[[i]])) + 
  scale_color_manual(values = points$color) +
  theme_void() + theme(plot.title=element_text(margin = margin(b=10), hjust = 0.45))
}

```

## Step 6: Produce Plots!

```{r}

# Plot cleveland bar plot
cleveland <- metro_grades %>% filter(metro_area == "Cleveland-Elyria, OH") %>% select(holc_grade, pct_white, pct_black, pct_hisp, pct_asian, pct_other) %>% pivot_longer(pct_white:pct_other)
cleveland$holc_grade <- factor(cleveland$holc_grade, levels=rev(c("A","B","C","D")))
cleveland$holc_grade <- recode(cleveland$holc_grade, A="\"Best\"", B="\"Desirable\"", C="\"Declining\"", D="\"Hazardous\"")
cleveland$name <- recode(cleveland$name, pct_white="White", pct_black="Black", pct_hisp="Latino", pct_asian="Asian", pct_other = "Other")
cleveland$name <- factor(cleveland$name, levels=rev(c("White", "Black", "Latino", "Asian", "Other")))

ggplot(cleveland) + geom_bar(aes(x = value, y = holc_grade, fill = name), color="white", lwd=1, width=0.8, stat="identity", show.legend=T) +
  theme_void() +
  theme(axis.text.y = element_text(),
        legend.position="top",
        legend.title=element_blank()) +
  scale_fill_manual(guide=guide_legend(reverse=T), values = rev(points$color))

```

```{r, out.width="100%"}
### DIFFERENT STYLE FROM ARTICLE ###

metros_A <- metro_grades %>% filter(holc_grade == grade)
  
  # Turn the points into longitude and latitude so we can repel the points on the ggplot
  metros_A$lon <- map_dbl(metros_A$centroid, function(x){x[[1]]})
  metros_A$lat <- map_dbl(metros_A$centroid, function(x){x[[2]]})
  metros_A$pct_nonwhite <- 100 - metros_A$pct_white
  metros_A$rad <- (metros_A$value^(1/3)) / 5000

nation_pie <- function(metro_grades, grade){
  metros_A <- metro_grades %>% filter(holc_grade == grade)
  
  # Turn the points into longitude and latitude so we can repel the points on the ggplot
  metros_A$lon <- map_dbl(metros_A$centroid, function(x){x[[1]]})
  metros_A$lat <- map_dbl(metros_A$centroid, function(x){x[[2]]})
  metros_A$pct_nonwhite <- 100 - metros_A$pct_white
  metros_A$rad <- (metros_A$value^(1/3)) / 200
  
  mas <- metros_A %>% select(lon, lat, pct_white, pct_nonwhite, value, rad) %>% arrange(desc(value))
  
  end <- nrow(mas)
  for(i in 1:(nrow(mas)-1)){
    cur <- mas[i,]
    lon_dist <- cur$lon - mas$lon[(i+1):end]
    lat_dist <- cur$lat - mas$lat[(i+1):end]
    dists <- sqrt((lon_dist)^2 + (lat_dist)^2)
    
    move <-  mas$rad[i] / dists
    move[move <= 1] <- 0
    
    mas$lon[(i+1):end] <- mas$lon[(i+1):end] - lon_dist*move
    mas$lat[(i+1):end] <- mas$lat[(i+1):end] - lat_dist*move
  }
  
  title <- ifelse(grade == "A", "Best", "Hazardous")
  
  ggplot() + 
    ggtitle(title) + 
    geom_sf(data=filter(states, !(NAME %in% c("Alaska", "Hawaii", "Puerto Rico"))) , mapping = aes(geometry = geometry)) +
    #geom_jitter(data=metros_A, mapping = aes(x = lon, y = lat)) + 
    geom_scatterpie(data=mas, 
                    mapping = aes(x = lon, y = lat, r = rad), 
                    cols=c("pct_white", "pct_nonwhite"), 
                    color = "white", show.legend=F) + 
    scale_fill_manual(values = c("#ffb262","#808285")) +
    theme_void() + 
    theme(plot.title = element_text(hjust = 0.5))
}

A <- nation_pie(metro_grades, "A")
D <- nation_pie(metro_grades, "D")
grid.arrange(A, D, nrow=1)


```



# Pittsburgh, PA: {.tabset .tabset-pills}

## "BEST" 

```{r, echo=F, out.width="49%", warning = F}
holc_plots[["A"]]
construct_surrounding_plot(surrounding_area, PA_plot)

```


```{r, echo=F, out.width="100%", warning = F}
# Note that we need a second code block since plotly objects can't use out.width
subplot(bar_grade(metro_grades, "A"), surrounding_bar, nrows=1)

```

## "DESIRABLE" 

```{r, echo=FALSE, out.width="49%", warning = FALSE}
holc_plots[["B"]]
construct_surrounding_plot(surrounding_area, PA_plot)
```

```{r, echo=F, out.width="100%", warning = F}
subplot(bar_grade(metro_grades, "B"), surrounding_bar, nrows=1)
```

## "DECLINING" 

```{r, echo=FALSE, out.width="49%", warning = FALSE}
holc_plots[["C"]]
construct_surrounding_plot(surrounding_area, PA_plot)
```

```{r, echo=F, out.width="100%", warning = F}
subplot(bar_grade(metro_grades, "C"), surrounding_bar, nrows=1)
```

## "HAZARDOUS" 

```{r, echo=FALSE, out.width="49%", warning = FALSE}
holc_plots[["D"]]
construct_surrounding_plot(surrounding_area, PA_plot)
```

```{r, echo=F, out.width="100%", warning = F}
subplot(bar_grade(metro_grades, "D"), surrounding_bar, nrows=1)
```